Cellct analysis

### 2019-11-04 code/cellcount.Rmd
changes

```{r heatmap, echo=F, fig.height=10, fig.width=6}
p <- cellct %>% 
  left_join(field, by="sample_id")

morpho_order <- c("Green cell",
                  "Sanguina 'citrine'",
                  "Sanguina nivaloides",
                  "Sanguina nivaloides 'ruby'",
                  "Green cell",
                  "Chlainomonas",
                  "Chloromonas krienitzii",
                  "Chloromonas cf. brevispina",
                  "Chloromonas cf. nivalis",
                  "Chloromonas 'spiny'",
                  "Chloromonas 'oval'",
                  "Chloromonas 'zuke'"
                  )

my_theme <- theme(axis.text.x = element_text(hjust=1,angle=45))

ggplot(p, aes(y=alias %>% fct_reorder(elev_m), 
              x=morpho_sp)) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp)) + # color = "white" %>% fct_reorder(morpho_order)
  labs(x="Cell morphology", y= "Sample ID", fill = "Cell morphology", alpha="Relative abundance") +
  guides(fill=F) +
  scale_alpha(range = c(0.1, 1)) +
  my_theme
```

>>>>

```{r heatmap, echo=F, fig.height=5, fig.width=3}
p <- cellct %>% 
  left_join(field, by="sample_id")

short_names <- p %>% 
  mutate(short_morpho_name = case_when(morpho_sp=="Chlainomonas"~"Cr",
                                       morpho_sp=="Chloromonas cf. brevispina"~"Cb",
                                       morpho_sp=="Chloromonas cf. nivalis"~"Cn",
                                       morpho_sp=="Chloromonas krienitzii"~"Ck",
                                       morpho_sp=="Green cell"~"G",
                                       morpho_sp=="Other"~"O",
                                       morpho_sp=="Sanguina nivaloides"~"Sn"))

my_theme <- theme(axis.title.y =element_blank(),
                  axis.text.y=element_blank(),
                  axis.ticks.y=element_blank(), 
                  legend.position = "none")

cellct_heatmap <- ggplot(short_names, aes(y=alias %>% fct_reorder(elev_m), 
              x=short_morpho_name)) +
  geom_tile(aes(alpha = percent_of_sample, fill = morpho_sp)) + # color = "white" %>% fct_reorder(morpho_order)
  labs(x="Cell morphology", y= "Sample ID (in order of elevation)", fill = "Cell morphology", alpha="Relative abundance") +
  scale_alpha(range = c(0.1, 1)) +
  guides(alpha=FALSE)+
  my_theme

cellct_heatmap
```

```{r, elevation_bar, echo=F}
elevation_ranges <- short_names %>% 
  distinct(elev_m, sample_id) %>% 
  arrange(elev_m)

ggplot(elevation_ranges, aes(x=sample_id %>% fct_reorder(elev_m), y=elev_m))+
  geom_bar(stat = "identity")+
  coord_flip()
```

```{r}
ggsave(filename=here("manuscript/figs/1_field/cellct_heatmap.pdf"), plot=cellct_heatmap, height = 7, width = 2)
```
